COG-ED Manuscript

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd

## Procedure

>>>>

## Procedure
Participants for the pilot study were recruited using the software *ORSEE* [@Greiner2015].
The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires at least two days after the second session.
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
After each level, participants filled out the NASA-TLX questionnaire [@Hart1988] on a tablet to assess their perceived task load.
Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behaviour in the ED procedure, so the n-back data of this part was not analyzed.
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task, ED procedure, and repetition of a random "level" as in session one.
There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
Two days after the second session, participants received a link to the personality questionnaires (only the NFC scale [@Bless1994; @Cacioppo1984] was analyzed in the present study, the full list of questionnaires can be found in Appendix 1).
Participants received 8€ per hour, about 30€ in total, or course credit for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
